---
title: "Disparities in the impacts of co-management on fishers' livelihoods"
author: "Ruano-Chamorro et al."
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
INEQ = read.csv("INEQ_22.csv",
                header = TRUE,
                dec = ".")
```

### LOAD PACKAGES

```{r "load packages"}

library(ggplot2) # An Implementation of the Grammar of Graphics
library(gridExtra) # Miscellaneous Functions for "Grid" Graphics
library(lattice) # Trellis Graphics for R
library(lme4) # Linear Mixed-Effects Models using 'Eigen' and S4
library(arm)
library(scales) # Scale Functions for Visualization
library(performance)
library(DHARMa)
library(insight)
library(parameters)
library(sjPlot)
library(tidyverse)
library(graphics)
library(vcd)
library(ggstatsplot)
library(dplyr)
library(ggpubr)
library(MuMIn)
library(car)
```

### PREPARE DATA FOR ANALYSIS


Meaning of variables:
  - site = community
  - OrgEffLivelihood = Impact on individual livelihoods. 5 point likert scale
  - OrgEffComm = Impact on community. 5 point likert scale
  - yrseducation = years of education
  - migrant = being a migrant or not
  - marlivprim = fishing is a primary livelihood
  - occdiv = occupational diversity
  - mslall = wealth, material life style
  - trustleaders = trust on leaders
  - decispart = level of participation in decision-making processes
  - CommEvent = participation in community events
  - popn = population size
  - distmktreg = distance to markets
  - regr = presence or abcense of gear restrictions
  - regg = presence or abcense of acces restriction
  - rega =  presence or abcense ofarea restriction
  - clearboundaries = presence or abcense of clear boundaries
  - confmechinter = conflic resolution mechanisms
  - GradSanctions = presence or abcense of graduated sanctions



Eliminate don't knows and NAs from OrgEffLivelihood and OrgEffComm.

```{r }
str(INEQ$OrgEffLivelihood)
INEQ$OrgEffLivelihood_cat<-as.factor(INEQ$OrgEffLivelihood)
str(INEQ$OrgEffComm)
INEQ$OrgEffComm_cat<-as.factor(INEQ$OrgEffComm)

ggplot(INEQ,aes(OrgEffLivelihood_cat))+geom_bar()#there are more than 150 don't knows
ggplot(INEQ,aes(OrgEffComm_cat))+geom_bar()#there are almost 200 don't knows

#eliminate don' knows
INEQ <- INEQ[INEQ$OrgEffLivelihood!=0,]
INEQ <- INEQ[INEQ$OrgEffComm!=0,]

#eliminate NAs

which(is.na(INEQ$OrgEffLivelihood))
INEQ<-INEQ[-c(847, 858, 882, 895, 904, 906, 927, 960),]

which(is.na(INEQ$OrgEffComm))

colSums(is.na(INEQ))

dim(INEQ)#968

```
### Calculate disparity 

In this script disparity = inequality


####################################### CALCULATE DISPARITY 1 (OBJECTIVE) #######################################

Disparity 1 (Objective disparity) = (how the individual think he/she benefits from co-management) - (average of how individuals think they benefit from co-management) 



```{r }

# Inequality1 = OrgEffLivelihood - average at community level of all OrgEffLivelihood
avgeffliv.table <- setNames(aggregate(as.numeric(INEQ$OrgEffLivelihood)~INEQ$site,FUN=mean),c("site","avgeffliv"))#table with averages of how individual think they benefit per site ("objective measure" of how the community benefits)
INEQ.outcomes <- merge(INEQ,avgeffliv.table, by = intersect("site", "site"), all=FALSE) #average has been added to the data frame INEQ
INEQ.outcomes$Inequality1_rec = as.numeric(INEQ.outcomes$OrgEffLivelihood) - as.numeric(INEQ.outcomes$avgeffliv)


```

####################################### CALCULATE DISPARITY 2 (SUBJECTIVE/PERCEIVED) #######################################

Disparity 2 (Subjective disparity, or perceived disparity) = (how the individual think he/she benefits from co-management) - (how the individual thinks the community benefits)

```{r }

 # Calculate Inequality2 (OrgEffLivelihood - OrgEffComm)
INEQ.outcomes$Inequality2_rec = as.numeric(INEQ.outcomes$OrgEffLivelihood) - as.numeric(INEQ.outcomes$OrgEffComm)

# check distribution of new response variables
par(mfrow = c(1,2),mar=c(2,2,2,2))
hist(INEQ.outcomes$Inequality1_rec,main="Inequality1 (recalculated)",breaks = c(-5,-4,-3,-2,-1,0,1,2,3,4,5))
hist(INEQ.outcomes$Inequality2_rec,main="Inequality2 (recalculated)",breaks = c(-5,-4,-3,-2,-1,0,1,2,3,4,5))

INEQ=INEQ.outcomes

```

###################### TYPE OF DISPARITY #######################


```{r }


### Split Disparity1 data into losses (-5 to 0)  and gains (0 to 5)
# 1. Create binary variable: 0 for equal, 1 for any disparity
INEQ$Ineq1_bin <- as.integer(ifelse(INEQ$Inequality1_rec < 0.5 & INEQ$Inequality1_rec > -0.5,0,1))#tranform to 0 values between 0.5 and -0.5 (equality), tranform to 1 the rest 


#2. Create categorical variable with type of disparity: "equal", "loss", "gain"
INEQ$Ineq1_bintype <- as.factor(ifelse(INEQ$Inequality1_rec < -0.5,"loss", 
                                       ifelse(INEQ$Inequality1_rec>0.5,"gain","equal")))

### Split Disparity2 data into losses (-5 to 0)  and gains (0 to 5)
# 1. Create binary variable: 0 for equal, 1 for any disparity
INEQ$Ineq2_bin <- as.integer(ifelse(INEQ$Inequality2_rec == 0,0,1))
# 2. Create categorical variable with type of disparity: "equal", "loss", "gain"
INEQ$Ineq2_bintype <- as.factor(ifelse(INEQ$Inequality2_rec < 0,"loss", 
                                       ifelse(INEQ$Inequality2_rec>0,"gain","equal")))



```




Eliminate rest of dont'knows and NAs

```{r }

which(is.na(INEQ$trustleaders))
INEQ<-INEQ[-c(597),]#eliminate NAs

INEQ <- INEQ[INEQ$trustleaders!=0,] #Eliminate don't knows


which(is.na(INEQ$ yrseducation))

INEQ<-INEQ[-c(906),] #eliminate NAs


which(is.na(INEQ$migrant))

INEQ<-INEQ[-c(913),] #eliminate NAs

which(is.na(INEQ$ decispart ))
INEQ<-INEQ[-c(237,485),] #eliminate NAs
colSums(is.na(INEQ))

colSums(is.na(INEQ))

dim(INEQ)#955


#oultiers community events

boxplot(INEQ$CommEvent, plot=FALSE)$out  #Identify the outliers

hist(INEQ$CommEvent)

which(is.na(INEQ$ CommEvent )) #Identify NAs in community events

INEQ<-INEQ[-c(99, 207, 210, 213, 214, 215, 217, 218, 220, 231, 250, 257, 379, 403, 404, 
               406, 408, 409, 410, 413, 454, 501, 549, 607, 610, 623, 669, 670, 672, 677, 795, 852, 949, 954),]  #eliminate NAs


colSums(is.na(INEQ))

INEQ<-subset(INEQ,CommEvent<18)#Eliminate this outlier. It is an error

dim(INEQ)#920


which(is.na(INEQ$ CommEvent ))


```

Define factors and standardize predictors


```{r }
# Factors should be treated as such in the analysis

INEQ$decispart_cat <- as.factor(INEQ$decispart)
INEQ$sex_cat<-as.factor(INEQ$sex)
INEQ$site_cat<-as.factor(INEQ$site)
INEQ$migrant_cat<-as.factor(INEQ$migrant)
INEQ$marlivprim_cat<-as.factor(INEQ$marlivprim)
INEQ$regr_cat<-as.factor(INEQ$regr)
INEQ$regg_cat<-as.factor(INEQ$regg)
INEQ$rega_cat<-as.factor(INEQ$rega)
INEQ$GradSanctions_cat<-as.factor(INEQ$GradSanctions)
INEQ$clearboundaries_cat<-as.factor(INEQ$clearboundaries)
```

Standardize predictors
```{r }
#continuous

#standardize (2sd) 
INEQ$distmktreg_sd<-scale(INEQ$distmktreg)*0.5
INEQ$popn_sd<-scale(INEQ$popn)*0.5
INEQ$yrseducation_sd<-scale(INEQ$yrseducation)*0.5
INEQ$mslall_sd<-scale(INEQ$mslall)*0.5
INEQ$occdiv_sd<-scale(INEQ$occdiv)*0.5
INEQ$CommEvent_sd<-scale(INEQ$CommEvent)*0.5
INEQ$trustleaders_sd<-scale(INEQ$trustleaders)*0.5
INEQ$confmechinter_sd<-scale(INEQ$confmechinter)*0.5

```

SPLIT DATA SET IN 4

Split initial INEQ dataset into 4 datasets that will be used in the models: losses and gains for Inequality 1 (actual) and Inequality 2 (perceived)
The 4 data sets are: 
1) INEQ_loss1 (for objective losses)
2) INEQ_gain1 (for objective gains)
3) INEQ_loss2 (for subjective losses)
4) INEQ_gain2 (for subjective gains)



```{r }


# LOSSES 1 (actual/objective): table containing only data for losses and equality for Inequality1

INEQ_loss1 <- INEQ[INEQ$Ineq1_bintype %in% c("loss","equal"),]
INEQ_loss1$site <- factor(INEQ_loss1$site)
INEQ_loss1$country <- factor(INEQ_loss1$country)

# GAINS 1 (actual): table containing only data for gains and equality for Inequality1
INEQ_gain1 <- INEQ[INEQ$Ineq1_bintype %in% c("gain","equal"),]
INEQ_gain1$site <- factor(INEQ_gain1$site)
INEQ_gain1$country <- factor(INEQ_gain1$country)


# LOSSES 2 (perceived): table containing only data for losses and equality for Inequality2
INEQ_loss2 <- INEQ[INEQ$Ineq2_bintype %in% c("loss","equal"),]
INEQ_loss2$site <- factor(INEQ_loss2$site)
INEQ_loss2$country <- factor(INEQ_loss2$country)
# GAINS 2 (perceived): table containing only data for gains and equality for Inequality2
INEQ_gain2 <- INEQ[INEQ$Ineq2_bintype %in% c("gain","equal"),]
INEQ_gain2$site <- factor(INEQ_gain2$site)
INEQ_gain2$country <- factor(INEQ_gain2$country)
```


### MODELS



### MODEL OBJECTIVE LOSSES (Disparity 1)



Define the global model

```{r}
M.loss1_global.model<-glmer(Ineq1_bin ~ migrant_cat+ sex_cat + yrseducation_sd + trustleaders_sd + decispart_cat + marlivprim_cat + mslall_sd + occdiv_sd + CommEvent_sd+ popn_sd + distmktreg_sd  +  regr_cat + regg_cat + rega_cat + clearboundaries_cat  + confmechinter_sd + GradSanctions_cat +(1 | site_cat), 
                                  data = INEQ_loss1,family=binomial(link = "logit"), na.action='na.fail',
                                  control = glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=1000000))) 
```


```{r}
summary(M.loss1_global.model)
```


```{r}
vif(M.loss1_global.model)
```

We can conclude there is not multicollinearity

```{r}
check_overdispersion(M.loss1_global.model)
```
```{r }
check_singularity(M.loss1_global.model)#singularity is fine
```
```{r }
check_convergence(M.loss1_global.model)#convergence is fine
```

```{r }
resid.loss1=simulateResiduals(M.loss1_global.model, plot=TRUE)
```





```{r}
#loss1.dredge<-dredge(global.model = M.loss1_global.model, trace = TRUE)#This line of code was run on the HPC of James Cook University. It will take a long time to run. Consider running this code in your own computer.
```

```{r}
loss1.2_dredge_sd<-readRDS(file="loss1.2.dredge.sd.rds")
```

Model average
```{r}
loss1.average_sd<-summary(model.avg(loss1.2_dredge_sd, subset = delta <= 2))
```


```{r}
loss1.average_sd
```
Relative influence
```{r}
sw(loss1.average_sd)#Sum of model weights over all models including each explanatory variable.
```

Confident intervals of the full model
```{r}
confint(loss1.average_sd,full=T,level=0.9) #full model averages
```



```{r}
ma.loss1<-summary(loss1.average_sd)#pulling out model averages
```

```{r}
df.loss1<-as.data.frame(ma.loss1$coefmat.full)#selecting full model coefficient averages
```

```{r}
CI<-as.data.frame(confint(loss1.average_sd,level=0.9,full=T))# to get confident intervals for full model
```

```{r}
CI
```


```{r}
df.loss1$CI.min <-CI$`5 %` #pulling out CIs and putting into same df as coefficient estimates
```

```{r}
df.loss1$CI.max <-CI$`95 %`
```


```{r}
library('data.table')
```
```{r}
df.loss1
```


```{r}
setDT(df.loss1, keep.rownames='coefficient')#put row names into columns
```


```{r}
names(df.loss1) <- gsub(" ",'',names(df.loss1))#remove spaces from column headers
```



```{r}
ggplot(data=df.loss1, aes(x=coefficient, y=Estimate))+
  geom_hline(yintercept=0, color='grey', linetype='dashed', lwd=1)+
  geom_errorbar(aes(ymin=Estimate-Std.Error, ymax=Estimate+Std.Error), colour="pink",#SE
         width=.1, lwd=1)+
    coord_flip()+
    geom_point(size=3)+theme_classic(base_size=20)+xlab("")+
  geom_errorbar(aes(ymin=CI.min, ymax=CI.max), colour="blue", # CIs
                width=.2,lwd=1) 
  
```



###   MODEL OBJECTIVE GAINS (Disparity 1)

Define global model


```{r}
M.gains1_global.model<-glmer(Ineq1_bin ~ migrant_cat+ sex_cat + yrseducation_sd + trustleaders_sd + decispart_cat + marlivprim_cat + mslall_sd + occdiv_sd + CommEvent_sd+ popn_sd + distmktreg_sd  +  regr_cat + regg_cat + rega_cat + clearboundaries_cat  + confmechinter_sd + GradSanctions_cat +(1 | site_cat), 
                                  data = INEQ_gain1,family=binomial(link = "logit"), na.action='na.fail',
                                  control = glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=1000000))) 
```

```{r}
summary(M.gains1_global.model)
```
```{r}
check_overdispersion(M.gains1_global.model)
```
```{r }
check_singularity(M.gains1_global.model)
```
```{r }
check_convergence(M.gains1_global.model)
```

```{r }
resid.loss1=simulateResiduals(M.gains1_global.model, plot=TRUE,quantreg = T)
```
the qq-plot is nearly linear, suggesting that the overall distribution is roughly OK, also the res ~ fitted looks approximately OK. We will plot the residuals against the predictors to check if there is a pattern.

```{r }

#PLOT RESIDUALS FOR EACH PREDICTOR

ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=confmechinter_sd))+geom_point()
```
```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=trustleaders_sd))+geom_point()
```
```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=migrant_cat))+geom_point()
```
```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=sex_cat))+geom_point()
```

```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=yrseducation_sd))+geom_point()
```
```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=decispart_cat ))+geom_point()
```
    ```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=marlivprim_cat))+geom_point()
```


```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= mslall_sd ))+geom_point()
```
```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=    occdiv_sd ))+geom_point()
```
```{r }
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=   CommEvent_sd))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= popn_sd ))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= regr_cat))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= regg_cat))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= rega_cat))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x=   clearboundaries_cat))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= confmechinter_sd))+geom_point()
```
```{r}
ggplot(data=INEQ_gain1, aes(y=resid(M.gains1_global.model),x= GradSanctions_cat ))+geom_point()
```
  



```{r}
vif(M.gains1_global.model)
```


```{r}
#gains1.dredge<-dredge(global.model = M.gains1_global.model, trace = TRUE)#This line of code was run on the HPC of James Cook University. It will take a long time to run. Consider running this code in your own computer.
```


```{r}
gains1.2_dredge_sd<-readRDS(file="gains1.2.dredge.sd.rds")
```



```{r}
gains1.average_sd<-summary(model.avg(gains1.2_dredge_sd, subset = delta <= 2))
```



```{r}
gains1.average_sd
```

```{r}
sw(gains1.average_sd)
```

```{r}
confint(gains1.average_sd,full=T,level=0.9) #full model averages
```


```{r}
ma.gains1<-summary(gains1.average_sd)#pulling out model averages
```

```{r}
df.gains1<-as.data.frame(ma.gains1$coefmat.full)#selecting full model coefficient averages
```

```{r}
CI<-as.data.frame(confint(gains1.average_sd,level=0.9,full=T))# to get confident intervals for full model
```

```{r}
CI
```

```{r}
df.gains1$CI.min <-CI$`5 %` #pulling out CIs and putting into same df as coefficient estimates
```

```{r}
df.gains1$CI.max <-CI$`95 %`
```


```{r}
df.gains1
```

```{r}
setDT(df.gains1, keep.rownames='coefficient')#put row names into columns
```


```{r}
names(df.gains1) <- gsub(" ",'',names(df.gains1))#remove spaces from column headers
```





```{r}
ggplot(data=df.gains1, aes(x=coefficient, y=Estimate))+
  geom_hline(yintercept=0, color='grey', linetype='dashed', lwd=1)+
  geom_errorbar(aes(ymin=Estimate-Std.Error, ymax=Estimate+Std.Error), colour="pink",#SE
         width=.1, lwd=1)+
    coord_flip()+
    geom_point(size=3)+theme_classic(base_size=20)+xlab("")+
  geom_errorbar(aes(ymin=CI.min, ymax=CI.max), colour="blue", # CIs
                width=.2,lwd=1) 
  
```

###  MODEL SUBJECTIVE LOSSES (Disparity 2)

```{r}
M.loss2_global.model<-glmer(Ineq2_bin ~ migrant_cat+ sex_cat + yrseducation_sd + trustleaders_sd + decispart_cat + marlivprim_cat + mslall_sd + occdiv_sd + CommEvent_sd+ popn_sd + distmktreg_sd  +  regr_cat + regg_cat + rega_cat + clearboundaries_cat  + confmechinter_sd + GradSanctions_cat +(1 | site_cat), 
                                  data = INEQ_loss2,family=binomial(link = "logit"), na.action='na.fail',
                                  control = glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=1000000))) 
```

```{r}
summary(M.loss2_global.model)
```

```{r}
check_overdispersion(M.loss2_global.model)
```
```{r }
check_singularity(M.loss2_global.model)
```
```{r }
check_convergence(M.loss2_global.model)
```

```{r }
resid.loss1=simulateResiduals(M.loss2_global.model, plot=TRUE)
```

```{r}
vif(M.loss2_global.model)
```




```{r}
#loss2.dredge<-dredge(global.model = M.loss2_global.model, trace = TRUE)#This line of code was run on the HPC of James Cook University. It will take a long time to run. Consider running this code in your own computer.
```

```{r}
loss2.2_dredge_sd<-readRDS(file="loss2.2.dredge.sd.rds")
```


average model


```{r}
loss2.average_sd<-summary(model.avg(loss2.2_dredge_sd, subset = delta <= 2))
```


```{r}
loss2.average_sd
```


```{r}
sw(loss2.average_sd)
```


```{r}
confint(loss2.average_sd,full=T,level=0.9) #full model averages
```


```{r}
ma.loss2<-summary(loss2.average_sd)#pulling out model averages
```

```{r}
df.loss2<-as.data.frame(ma.loss2$coefmat.full)#selecting full model coefficient averages
```

```{r}
CI<-as.data.frame(confint(loss2.average_sd,level=0.9,full=T))# to get confident intervals for full model
```

```{r}
CI
```


```{r}
df.loss2$CI.min <-CI$`5 %` #pulling out CIs and putting into same df as coefficient estimates
```

```{r}
df.loss2$CI.max <-CI$`95 %`
```



```{r}
df.loss2
```


```{r}
setDT(df.loss2, keep.rownames='coefficient')#put row names into columns
```


```{r}
names(df.loss2) <- gsub(" ",'',names(df.loss2))#remove spaces from column headers
```



```{r}
ggplot(data=df.loss2, aes(x=coefficient, y=Estimate))+
  geom_hline(yintercept=0, color='grey', linetype='dashed', lwd=1)+
  geom_errorbar(aes(ymin=Estimate-Std.Error, ymax=Estimate+Std.Error), colour="pink",#SE
         width=.1, lwd=1)+
    coord_flip()+
    geom_point(size=3)+theme_classic(base_size=20)+xlab("")+
  geom_errorbar(aes(ymin=CI.min, ymax=CI.max), colour="blue", # CIs
                width=.2,lwd=1) 
  
```





###  MODEL SUBJECTIVE GAINS (Disparity 2)

 Define global model


```{r}
M.gains2_global.model<-glmer(Ineq2_bin ~ migrant_cat+ sex_cat + yrseducation_sd + trustleaders_sd + decispart_cat + marlivprim_cat + mslall_sd + occdiv_sd + CommEvent_sd+ popn_sd + distmktreg_sd  +  regr_cat + regg_cat + rega_cat + clearboundaries_cat  + confmechinter_sd + GradSanctions_cat +(1 | site_cat), 
                                  data = INEQ_gain2,family=binomial(link = "logit"), na.action='na.fail',
                                  control = glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=1000000))) 
```


```{r}
summary(M.gains2_global.model)
```
```{r}
check_overdispersion(M.gains2_global.model)
```
```{r }
check_singularity(M.gains2_global.model)
```
```{r }
check_convergence(M.gains2_global.model)
```

```{r }
resid.loss1=simulateResiduals(M.gains2_global.model, plot=TRUE)
```
```{r}
vif(M.gains2_global.model)
```



```{r}
#gains2.dredge<-dredge(global.model = M.gains2_global.model, trace = TRUE) #This line of code was run on the HPC of James Cook University. It will take a long time to run. Consider running this code in your own computer.
```

```{r}
gains2.2_dredge_sd<-readRDS(file="gains2.2.dredge.sd.rds")
```



```{r}
gains2.average_sd<-summary(model.avg(gains2.2_dredge_sd, subset = delta <= 2))
```


```{r}
gains2.average_sd
```

```{r}
sw(gains2.average_sd)
```


```{r}
confint(gains2.average_sd,full=T,level=0.9) #full model averages
```


```{r}
ma.gains2<-summary(gains2.average_sd)#pulling out model averages
```

```{r}
df.gains2<-as.data.frame(ma.gains2$coefmat.full)#selecting full model coefficient averages
```

```{r}
CI<-as.data.frame(confint(gains2.average_sd,level=0.9,full=T))# to get confident intervals for full model
```

```{r}
CI
```


```{r}
df.gains2$CI.min <-CI$`5 %` #pulling out CIs and putting into same df as coefficient estimates
```

```{r}
df.gains2$CI.max <-CI$`95 %`
```



```{r}
df.gains2
```


```{r}
setDT(df.gains2, keep.rownames='coefficient')#put row names into columns
```


```{r}
names(df.gains2) <- gsub(" ",'',names(df.gains2))#remove spaces from column headers
```



```{r}
ggplot(data=df.gains2, aes(x=coefficient, y=Estimate))+
  geom_hline(yintercept=0, color='grey', linetype='dashed', lwd=1)+
  geom_errorbar(aes(ymin=Estimate-Std.Error, ymax=Estimate+Std.Error), colour="pink",#SE
         width=.1, lwd=1)+
    coord_flip()+
    geom_point(size=3)+theme_classic(base_size=20)+xlab("")+
  geom_errorbar(aes(ymin=CI.min, ymax=CI.max), colour="blue", # CIs
                width=.2,lwd=1) 
  
```






